ERA5 Temperature and Humidity climatologies for regression analysis

### 2025-06-12 ERA5 data/1990-2020/ERA5_1990_2020.Rmd
update

url='http://apdrc.soest.hawaii.edu/dods/public_data/Reanalysis_Data/ERA5/daily_3d/'
humidity= xr.open_dataset(url+'Specific_humidity')
humidity=humidity.sel(time=slice("1990-01-01","2020-12-31"))
humidity= humidity.assign_coords(lon=(((humidity.lon + 180) % 360) - 180))
humidity=humidity.sel(lev=1000, lat=slice(20,60),lon=slice(-130,-60))
# xarray dataset
humidity.to_netcdf(path='ERA5_humidity_data_US_2010_2024.nc')
```
Plotting temperature and humidity NetCDFs.

>>>>

url='http://apdrc.soest.hawaii.edu/dods/public_data/Reanalysis_Data/ERA5/daily_3d/'
humidity= xr.open_dataset(url+'Specific_humidity')
humidity=humidity.sel(time=slice("1990-01-01","2020-12-31"))
humidity= humidity.assign_coords(lon=(((humidity.lon + 180) % 360) - 180))
humidity=humidity.sel(lev=1000, lat=slice(20,60),lon=slice(-130,-60))
# xarray dataset
humidity.to_netcdf(path='ERA5_humidity_data_US_2010_2024.nc')
```

After downloading the file you can use the code below to get mean weekly temperature for each state.

Plotting temperature and humidity NetCDFs.
